Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-12-13 paper.tex
Add exp setup details; closes #55

Experiments were performed in a turbine test bed specifically designed for
cross-flow turbines. The turbine model used in this study was the UNH Reference
Vertical Axis Turbine (RVAT), which was designed to be a generic case for
numerical model testing, similar to the Sandia National Labs/US Department of
Energy RM2 River Turbine \cite{Neary2014}, but with higher solidity, or blade
chord to radius ratio.

@@

The turbine was mounted in a frame constructed from NACA 0020 sections, shown in
Figure~\ref{fig:exp-setup}. The turbine shaft ran up through the water surface,
coupled to a permanent magnet servo motor with a 20:1 gearbox, providing precise
control over shaft RPM. This servo was controlled by the tow tank's main motion
controller for high synchronization with the carriage motion, thereby giving
precise measurement and control of tip speed ratio. A rotary torque transducer
was installed inline between the servo and the turbine, and the servo was also
mounted on a slewing ring bearing, which allowed a redundant measurement of
torque via an arm and load cell used to counteract the turbine moment. The frame
was mounted to the carriage via linear guides, such that the total streamwise
drag force was transferred to a pair of S-beam load cells, providing the rotor
drag measurements, after a measured tare drag was subtracted in post processing.
Similarly, a tare torque was measured by rotating the turbine shaft in air.
Turbine angular and tow carriage linear position were measured using quadrature
encoder signals, with $10^5$ counts-per-rev for the turbine and 10 $\mathrm{\mu
    m}$ resolution for the carriage position. These signals, along with the torque
and drag signals, were sampled at 2 kHz.

\begin{figure}[ht!]
\centering
\includegraphics[width=0.75\textwidth]{figures/exp_setup_drawing}
\caption{Experimental setup: turbine test bed installed in UNH tow tank.}
\label{fig:exp-setup}
\end{figure}

Wake velocity was measured using a Nortek Vectrino+ acoustic Doppler velocimeter
(ADV), sampling at 200 Hz. The probe was mounted on an automated positioning
system, also controlled by the tow tank's main motion controller. The ADV and
DAQ systems' sampling times were synchronized by triggering the start of data
acquisition via a pulse sent from the motion controller. Additional details of
the turbine and experimental setup are described in \cite{Bachant2015-JoT}.

>>>>

Experiments were performed in a turbine test bed specifically designed for
cross-flow turbines. The test bed was integrated as part of the UNH tow tank,
which is a 30 m long facility with a 3.66 m wide and 2.44 m deep cross-section.
The turbine model used in this study was the UNH Reference Vertical Axis Turbine
(RVAT), which was designed to be a generic case for numerical model testing,
similar to the Sandia National Labs/US Department of Energy RM2 River Turbine
\cite{Neary2014}, but with higher solidity, or blade chord-to-radius ratio.

@@

The turbine was mounted in a frame constructed from NACA 0020 sections, shown in
Figure~\ref{fig:exp-setup}. The turbine shaft ran up through the water surface,
coupled to a Kollmorgen AKM permanent magnet servo motor with a 20:1 gearbox,
providing precise control over shaft RPM. This servo was controlled by the tow
tank's main motion controller for high synchronization with the carriage motion,
thereby giving precise measurement and control of tip speed ratio. An Interface
T8 200 Nm capacity rotary torque transducer was installed inline between the
servo and the turbine, and the servo was also mounted on a slewing ring bearing,
which allowed a redundant measurement of torque via an arm and load cell used to
counteract the turbine moment. The frame was mounted to the carriage via linear
guides, such that the total streamwise drag force was transferred to a pair of
Sentran ZB3 500 lbf capacity S-beam load cells, providing the rotor drag
measurements, after a measured tare drag was subtracted in post processing.
Similarly, a tare torque was measured by rotating the turbine shaft in air.
Turbine angular and tow carriage linear position were measured using quadrature
encoder signals, with $10^5$ counts-per-rev for the turbine and 10 $\mathrm{\mu
    m}$ resolution for the carriage position. These signals, along with the torque
and drag signals, were sampled at 2 kHz.

    \includegraphics[width=0.8\textwidth]{figures/exp-setup-photo}

    \includegraphics[width=0.8\textwidth]{figures/exp_setup_drawing}

    \caption{Experimental setup: turbine test bed installed in UNH tow tank.}

    \label{fig:exp-setup}
\end{figure}

Wake velocity was measured using a Nortek Vectrino+ acoustic Doppler velocimeter
(ADV), which has a 6 mm diameter sampling volume, and sampled at 200 Hz. The
probe was mounted on an automated positioning system, also controlled by the tow
tank's main motion controller. The ADV and DAQ systems' sampling times were
synchronized by triggering the start of data acquisition via a pulse sent from
the motion controller. Additional details of the turbine and experimental setup
are described in \cite{Bachant2015-JoT}.
